The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts

### 2020-04-17 write-up/covid-writeup.tex
covid update

@@

@@

\subsection{Stratified sampling}

Suppose we stratify such that weighting is uninmportant.

>>>>

Prevalence is important in the long-run because the

@@

\emph{Increasing testing leads to lower correlation only if we see the gap $\Delta$ decrease.  If we just see $f$ }

@@

\subsection{Ration-based testing allocation}

We assume that the percentage of tests is rationed according to severity of symptoms.

Note that a person who displays severe symptoms may be COVID negative.
